%!TEX root = ../booklet.tex
% ^ leave for LaTeXTools build functionality

\begin{customPuzzle}{Opening ``Puzzle''}{Bungled Bureaucracy}{Overview}
  We're ready to get started solving some puzzles!... Unfortunately,
  there's a bit of \textbf{red tape} to clear up first.

  Due to legal reasons, any puzzle-solving on these premises
  must be approved through the proper channels,
  which requires a bit of paperwork to be completed.

  We'll provide each team with the required paperwork, which must
  be signed by the Puzzling Department. They should be located nearby,
  but they may not help you right away...

  This is totally not a puzzle (at least, due to legal reasons we
  cannot claim it is), but \textbf{we'll give your team
  \(100\) points anyway if you can get
  this bureaucratic nightmare cleared up within 30 minutes}.
  All you have to do is get your Important Paperwork signed.
  Easy, right?
  If you don't finish within that time limit, we may be able to pull
  some strings and let you start puzzling anyway (no promises, though).
  \textbf{
  In either case, return to Game HQ after this challenge to get started
  on the main Puzzles for the day.}
\end{customPuzzle}

\begin{customPuzzle}{Opening ``Puzzle''}{Bungled Bureaucracy}{Important Paperwork}
  Due to inexplicable
  federal regulations surrounding puzzle-solving, prospective puzzlers must
  first be approved by the local Puzzling Department. Only the Puzzling
  Department signature is required, but maybe you'll need to collect
  some other signatures too...

  {\Large
  \begin{tabular}{c|c}
    Department Name & Signature \hspace{15em} \\\hline\hline
    Puzzling Dept & \\\hline
    Complaints Dept & \\\hline
    Arguments Dept & \\\hline
    Insults Dept & \\\hline
    Dept of Silly Walks & \\\hline
  \end{tabular}
  }
\end{customPuzzle}

\begin{customPuzzle}{Opening Puzzle}{Bungled Bureaucracy}{Setup}
  FOR STAFF USE ONLY

  Spread out stations for each of the Departments throughout your
  play area. The Puzzling Dept should be the most out-of-the-way in order
  to spread out teams as they search around for it
  during the beginning of the puzzle.

  Each station should be given their appropriate instructions and briefed
  on their role in the puzzle before it begins.

  After explaining HSC16 rules to all the teams, introduce this puzzle by
  going over its Overview. Clearly explain the bounds for the puzzle so teams
  don't wander off too far. Remind players not to interfere with other
  teams trying to solve the puzzle, and if playing
  indoors remind them not to run.
  When you're ready, hand out a copy of Important
  Paperwork to each team and start their 30 minutes.

  When a team has gotten their paperwork signed by all five departments,
  they earn 100 points and should go to Game HQ to get their packet of
  the main Puzzles to take to their Team HQ.

  Give warnings at 15 and 5 minutes remaining to the players. If any team
  doesn't finish within 30 minutes, find them and let them know time is up,
  and get them started on the main Puzzles (they do not earn any points for
  the Opening Puzzle).
\end{customPuzzle}

\begin{customPuzzle}{Opening Puzzle}{Bungled Bureaucracy}{Puzzling Dept.}
  FOR STAFF USE ONLY

  When players attempt to have their Important Paperwork approved by
  you, inform them that all teams must include at least
  one member with a Photo ID proving
  that their birthday is on either February 30 or September 31.

  When they protest (even if they have photo ID,
  those dates don't exist),
  say that you get that a lot, but your hands are tied by the system.
  However, if they
  can get signatures from the other four departments, you can sign off on their
  paperwork anyway.

  When they return with all four signatures, sign their Important Paperwork.
  Tell them they are approved to start solving puzzles and can
  exchange their paperwork for a packet of puzzles at Game HQ.
\end{customPuzzle}

\begin{customPuzzle}{Opening Puzzle}{Bungled Bureaucracy}{Complaints Dept.}
  FOR STAFF USE ONLY

  As part of your character, you really don't want to be at work on a
  Saturday. So, make sure to complain as much as possible about that,
  as well as anything the players want you to do (this is the Complaints
  Dept, after all).

  If they ask you for a signature for the Puzzling Dept, tell them that you're
  just in too much of a bad mood to go through all that trouble. Ask them
  if they know of anything that will cheer you up.

  If they attempt a silly walk, chuckle a bit and ask them if their silly
  walk is certified. If not, stop laughing and gasp - obviously silly
  walks require a permit. Tell them that you'll find their silly walk
  much funnier if they get it certified.

  If they demonstrate a certified silly walk (i.e. they have the signature
  from the Dept of Silly Walks), you can sign their Important Paperwork.
\end{customPuzzle}

\begin{customPuzzle}{Opening Puzzle}{Bungled Bureaucracy}{Arguments Dept.}
  FOR STAFF USE ONLY

  As part of your character, you should contradict everything the players
  say. Tell them you will sign their Important Paperwork
  if they can say something you
  can't argue with. (You should accept anything reasonable.)

  If asked about new clubs starting up, break character and say you're
  really excited about the new Typography Club, and hand them a flyer.

  If asked about the Insults Dept., tell them they are quoting Monty Python
  and the Holy Grail.
\end{customPuzzle}

\begin{customPuzzle}{Opening Puzzle}{Bungled Bureaucracy}{Insults Dept.}
  FOR STAFF USE ONLY

  As part of your character, you should shout ``insults'' at the players.
  Keeping with the Monty Python theme (and keeping us out of trouble),
  stick to lines like these below (a French accent is optional):

  \begin{itemize}
  \item Your mother was a hamster and your father smelt of elderberries!
  \item I don't want to talk to you no more, you empty-headed animal food
    trough eaters!
  \item Now go away or I shall taunt you a second time!
  \item You don't frighten us, puzzling pig dogs.
  \item Go and boil your bottoms, you offspring of a silly person.
  \item I blow my nose in your general direction!
  \item You don't frighten us with your silly knees-bent running
    around puzzling!
  \end{itemize}

  You should sign their Important Paperwork if they can tell you what
  move you're quoting (Monty Python and the Holy Grail).

  If asked about it, you should tell the players
  that the Dept. of Silly Walks is going to be
  replaced to fund a new club, but you don't know which one. Tell the players
  that another department official may know more.
\end{customPuzzle}

\begin{customPuzzle}{Opening Puzzle}{Bungled Bureaucracy}{Dept. of Silly Walks}
  FOR STAFF USE ONLY

  As part of your character, you should have a silly walk that you use when
  moving around (and you should occassionally get up and walk your silly
  walk).

  If a player asks to certify a silly walk, say that it's not worth the trouble,
  since the host organization is dissolving the department tomorrow. You've
  heard it's going to be replaced, but you don't know by what. Tell the
  players you'll certify their silly walk if they bring evidence of whatever
  will be replacing your department's funding.

  If the players bring you a flyer for the Typography Club, you should
  get excited because you love fonts, apparently. (If they try to give you
  the flyer, say that they should hold onto it.) Ask to see their silly
  walk, and certify their silly walk by signing their Important Paperwork
  (no matter what they do).
\end{customPuzzle}
