%!TEX root = ../booklet.tex
% ^ leave for LaTeXTools build functionality

\begin{puzzle}
  Independence Graphcorp is a shipping company which specializes in volatile
  substances. By themselves, the below materials are stable; however,
  they can have rather... explosive reactions when transported with certain
  other chemicals. Help IG find the largest collection of chemicals which
  can be safely stored in the same truck for each of the following shipments.

  \begin{center}
  \fbox{\begin{minipage}{.7\linewidth}
  \textbf{Example Shipment:} Xereon, Olandrium, Karinum

  \begin{itemize}
    \item Xeroeon reacts with Olandrium, Karinum
    \item Olandrium reacts with Xeroeon
    \item Karinum reacts with Xeroeon
  \end{itemize}

  \textit{Example solution: Olandrium, Karinum}
  \end{minipage}}
  \end{center}

  \noindent
  \textbf{Shipment 1:} Unobtainum, Talcium, Hydreon, Silichrome, Electrax

  \begin{itemize}
    \item Unobtainum reacts with Talcium, Hydreon
    \item Talcium reacts with Unobtainum, Electrax
    \item Hydreon reacts with Unobtainum, Electrax, Silichrome
    \item Silichrome reacts with Hydreon
    \item Electrax reacts with Talcium, Hydreon
  \end{itemize}

  \noindent
  \textbf{Shipment 2:} Starogen, Talentium, Hardeox, Arometica, Kabbageon, Edax

  \begin{itemize}
    \item Starogen reacts with Talentium, Edax, Arometica
    \item Talentium reacts with Starogen, Kabbageon
    \item Hardeox reacts with Arometica, Kabbageon
    \item Arometica reacts with Starogen, Hardeox, Edax
    \item Kabbageon reacts with Talentium, Hardeox
    \item Edax reacts with Starogen, Arometica
  \end{itemize}


  \newpage

  \noindent
  \textbf{Shipment 3:} Undrax, Orangeon, Paxeox, Bargon, Grandogen, Restitin, Yandrian, Emporeon, Androxium, Nintindeon, Tarep, Segarium

  \begin{itemize}
    \item Undrax reacts with Orangeon, Yandrian
    \item Orangeon reacts with Yandrian, Undrax, Paxeox
    \item Paxeox reacts with Orangeon, Yandrian
    \item Bargon reacts with Grandogen
    \item Grandogen reacts with Bargon, Segarium
    \item Restitin reacts with Androxium, Tarep
    \item Yandrian reacts with Undrax, Orangeon, Paxeox
    \item Emporeon reacts with Nintindeon
    \item Androxium reacts with Restitin
    \item Nintindeon reacts with Emporeon, Segarium
    \item Tarep reacts with Restitin
    \item Segarium reacts with Grandogen, Nintindeon
  \end{itemize}


  \vfill

\noindent
The correct choices from each shipment can be used to spell out a word.
\textbf{Report the completed phrase to Game HQ to receive \(100\)
Victory Points.}


\vfill
\begin{center}
    \letterBox{}
    \letterBox{}
    \letterBox{}
    \hspace{1em}
    \letterBox{}
    \letterBox{}
    \letterBox{}
\end{center}
\begin{center}
    \letterBox{}
    \letterBox{}
    \letterBox{}
    \letterBox{}
    \letterBox{}
    \letterBox{}
    \letterBox{}
\end{center}
\vfill

\end{puzzle}

\begin{extraPuzzle}
Independence Graphcorp has one final shipment to make, it's a doozy.
What is the largest collection you can find of the following 30 products
(conveniently named Chemical-\(1\) through Chemical-\(30\))
which could be safely transported in the same vehicle?

  \begin{multicols}{2}
  \begin{itemize}
    \item 01 reacts with 03, 11, 18
    \item 02 reacts with 04, 21
    \item 03 reacts with 01, 30
    \item 04 reacts with 02, 19
    \item 05 reacts with 06, 07, 15
    \item 06 reacts with 05, 19, 30
    \item 07 reacts with 05, 10
    \item 08 reacts with 13, 25, 27
    \item 09 reacts with 12, 16, 23
    \item 10 reacts with 07, 15
    \item 11 reacts with 01, 17
    \item 12 reacts with 09
    \item 13 reacts with 08, 14, 26
    \item 14 reacts with 13
    \item 15 reacts with 05, 10, 28
    \item 16 reacts with 09
    \item 17 reacts with 11, 23, 30
    \item 18 reacts with 01, 20
    \item 19 reacts with 04, 06, 22
    \item 20 reacts with 18, 23
    \item 21 reacts with 02, 29
    \item 22 reacts with 19
    \item 23 reacts with 09, 17, 20
    \item 24 reacts with 26
    \item 25 reacts with 08, 29
    \item 26 reacts with 13, 24
    \item 27 reacts with 08, 28
    \item 28 reacts with 15, 27
    \item 29 reacts with 21, 25
    \item 30 reacts with 03, 06, 17
  \end{itemize}
  \end{multicols}

Submit this collection of numbers to Game HQ before the end of the game.
\textbf{The team(s) submitting the largest collection of numbers without
reactions will receive \(50\) Victory Points.} Teams which submit a collection of
numbers with even a single reaction will be disqualified, so be careful!

\begin{center}
    01 02 03 04 05 06 07 08 09 10

    11 12 13 14 15 16 17 18 19 20

    21 22 23 24 25 26 27 28 29 30
\end{center}
\end{extraPuzzle}



\begin{puzzleSolutions}
FOR STAFF USE ONLY

Main puzzle solution: ``USE THE UPBEATS''.

To grade the Extra,
check that no
two numbers cause a reaction according to the list given in EXTRA Puzzle 1.
Disqualify any submissions which this
checks. Otherwise, record the size of the submission; the largest submission
wins.
\end{puzzleSolutions}
