%!TEX root = ../scsu_handout.tex
% ^ leave for LaTeXTools build functionality

\begin{rules}

\heading{Schedule}

Here's an overview of the schedule for the day at
Southern Connecticut State University:

\begin{itemize}
\item Registration: \underline{Noon - 12:30pm}
\item Orientation: \underline{12:30pm - 1:00pm}
\item Opening Puzzle: \underline{1:00pm - 1:30pm}
\item Main Puzzles: \underline{1:30pm - 4:30pm}
\item Solutions Due: \underline{4:30pm}
\item Wrap-up, Awards, and Dismissal: \underline{4:30pm-5:00pm}
\end{itemize}

\vfill

\heading{Opening Puzzle}

If your school turned in a correct solution to the attached HSC16 teaser
puzzle, then your team will have a 90 second head start on our opening
challenge.

You'll want to find a solution to this conundrum as quickly as you can...
finishing within half an hour will earn your team
\(100\) Victory Points, and you'll immediately gain access to your Team Headquarters
and five new puzzles. After thirty minutes have passed, this challenge will end
and all remaining teams can move on to the rest of today's puzzles (but
will not earn any Victory Points).

\vfill

\heading{Main Puzzles}

After finishing the opening challenge, you'll receive a packet of
five Main Puzzles. Work
with your teammates on each puzzle to decode a hidden message. For each
correct solution you report to Game Headquarters, your team will earn \(100\)
Victory Points.

\vfill

\newpage

\heading{EXTRA Puzzles}

Five EXTRA Puzzles are hidden across your host campus! You'll need to
use the Campus MaPP, along with the solutions to the Main Puzzles, to
figure out where they are. When you think you know, check with Game HQ before
heading out to collect them.

Each EXTRA Puzzle is an added challenge based on the Main Puzzle which unlocked
it. Your goal is to optimize your solution as much as possible, because
the team(s) which submit today's best solution for each
to Game HQ before the end of the
competition will earn an extra \(50\) Victory Points.


\vfill


\heading{And more?}

Other hidden challenges may await you during the competition... you'll
have to join us to find out exactly what!


\vfill

\heading{End of the Game}

All solutions to Puzzles, EXTRA Puzzles, or anything else
are due at Game HQ at the time designated by the local director;
players not in line at Game HQ to submit a
solution will be turned away after that time.

All players and teachers/chaperones
from each team must be present for the wrap-up ten minutes
after the game ends to be eligible for awards.

\vfill

\heading{Winning the Game}

The team which has earned the most Victory Points by the end of the competition
is the winner. If two teams are tied for the same number of points,
then the team which solved the five Main Puzzles
quickest will be ranked higher. As an example:

\begin{center}
\begin{tabular}{c|c|c|c}
      & Team Alpha & Team Beta & Team Gamma \\\hline\hline
Opening Puzzle & solved at 12:05 & solved at 12:15 & solved at 12:10 \\\hline
Puzzle 1 & \textbf{solved at 3:00} & - & solved at 2:00 \\
Puzzle 2 & solved at 2:30 & solved at 2:15 & -  \\
Puzzle 3 & solved at 2:00 & solved at 2:30 & \textbf{solved at 2:45} \\
Puzzle 4 & - & solved at 2:40 & solved at 2:00 \\
Puzzle 5 & solved at 2:45 & - & solved at 2:15 \\\hline
Extra Puzzle 1 & best solution & - & - \\
Extra Puzzle 2 & - & best solution & - \\
Extra Puzzle 3 & - & best solution  & - \\
Extra Puzzle 4 & - & - & - \\
Extra Puzzle 5 & - & - & best solution \\\hline
Victory Points & 450 & 400 & 450 \\
Ranking & 2nd & 3rd & 1st
\end{tabular}
\end{center}

\vfill

\newpage

\heading{Additional Rules}

\begin{itemize}
\item The main rule is to be a good sport! Players should not do anything which
would interfere with other teams playing the game.
\item Teachers and chaperones are not allowed help players solve puzzles. However,
if the teams have any questions about how to interpret a puzzle, you should relay
those questions to the organizers.
\item Computers, smartphones, and the internet are not allowed to be used during
the competition.
\item Contact the game organizers in case of emergencies
or any issues with these rules.
\end{itemize}

\end{rules}