%!TEX root = ../booklet.tex
% ^ leave for LaTeXTools build functionality

\begin{about}
Thanks for downloading the puzzle booklet for
\textbf{High School Challenge '16} by Mathematical Puzzle Programs.
These puzzle materials are provided as-is for use in the classroom
(or anywhere else!)
to help showcase the fun of mathematical problem-solving. See the
\textit{Licensing} page for more details.

While the High School Challenge '16 is over,
we'd still love your feedback on how to improve this booklet. You can
contact us by email at info@mappmath.org. Or better yet,
submit an issue or pull request at our GitHub page at
\url{https://github.com/MaPPmath}
directly.

More information on Mathematical Puzzle Programs may be found at our website
\url{http://mappmath.org} and on our Twitter @MaPPmath. Happy mathematical puzzling!

- MaPP Directors and Volunteers
\end{about}


\begin{credits}
Mathematical Puzzle Programs staff
  \begin{itemize}
    \item Steven Clontz | Director
    \item Braxton Carrigan | Associate Director
    \item PJ Couch | Associate Director
    \item James Hammer | Associate Director
    \item Zachary Sarver | IT Consultant
  \end{itemize}

\noindent
High School Challenge '16 puzzle designers
  \begin{itemize}
    \item Jeffrey Ford | Minnesota State University, Mankato
    \item Kelly Bragan Guest | Tuskegee University
    \item Charles McPillan | Greenville, SC
    \item Jonah Ostroff | University of Washington
    \item Amy Steinkampf | New Orleans, LA
  \end{itemize}

\noindent
High School Challenge '16 host campuses
  \begin{itemize}
    \item Lamar University
    \item Southern Connecticut State University
    \item The University of North Carolina at Charlotte
  \end{itemize}

\noindent
Special Thanks
\begin{itemize}
  \item John Asplund
  \item Eric Harshbarger
  \item Robert Ford
\end{itemize}

\end{credits}

\begin{licensing}
  All rights to the content in this booklet are reserved by Mathematical
  Puzzle Programs until the conclusion
  of all High School Challenge '16 competitions.

  Following the conclusion of all High School Challenge '16 competitions,
  Mathematical Puzzle Programs licenses the content in this booklet
  under the Creative Commons Attribution 4.0
  International License. To view a copy of this license, visit

  \begin{center}
    \url{http://creativecommons.org/licenses/by/4.0/}
  \end{center}

  \vspace{2em}

  \noindent
  The following images in Puzzle 5 were reused under a
  Creative Commons Attribution-ShareAlike license (see links for details):
  \begin{itemize}
    \item https://commons.wikimedia.org/wiki/File:The\_11\_cubic\_nets.svg
    \item https://commons.wikipedia.org/wiki/File:Tetrahedron.jpg
    \item https://commons.wikimedia.org/wiki/File:Octahedron.svg
    \item https://commons.wikimedia.org/wiki/File:Icosahedron.jpg
    \item https://commons.wikimedia.org/wiki/File:Triangular\_dipyramid.png
    \item https://commons.wikimedia.org/wiki/File:Pentagonal\_dipyramid.png
    \item https://commons.wikimedia.org/wiki/File:Snub\_disphenoid.png
    \item https://commons.wikimedia.org/wiki/File:Triaugmented\_triangular\_prism.png
    \item https://commons.wikimedia.org/wiki/File:Gyroelongated\_square\_dipyramid.png
  \end{itemize}
\end{licensing}
